### 2014-06-19 alex/initial.Rmd
looking a top20 and bottom20

>>>>

Let's see if parent income has any effect on student performance.  No surprise here.
```{r parents, cache=TRUE}
library(ggvis)
students = student2012 %>% select(CNT, STIDSTD, math, read, sci)
parents = parent2012 %>% select(CNT, STIDSTD, PA07Q01,
                                PA03Q01, PA03Q02, PA03Q03, PA03Q04,
                                PA05Q01, PA05Q02, PA05Q03, PA05Q04)
student_parent = students %>% left_join(parents, by = c("STIDSTD", "CNT"))
student_parent = student_parent[!is.na(student_parent$PA07Q01), ]
qplot(x = PA07Q01, y = math, geom="boxplot", data = student_parent)
```

```{r time, cache=TRUE}
time_vars = c(paste0("ST57Q0", 1:6), "LMINS", "MMINS", "SMINS", "OUTHOURS", paste0("ST69Q0", 1:3), paste0("ST70Q0", 1:3), "ST71Q01")

#  ST57Q01                                       Out-of-School Study Time - Homework
#  ST57Q02                                Out-of-School Study Time - Guided Homework
#  ST57Q03                                 Out-of-School Study Time - Personal Tutor
#  ST57Q04                             Out-of-School Study Time - Commercial Company
#  ST57Q05                                    Out-of-School Study Time - With Parent
#  ST57Q06                                       Out-of-School Study Time - Computer
#172 ST69Q01	Min in <class period> - <test lang>
#173	ST69Q02	Min in <class period> - <Maths>
#174	ST69Q03	Min in <class period> - <Science>
#175	ST70Q01	No of <class period> p/wk - <test lang>
#176	ST70Q02	No of <class period> p/wk - <Maths>
#177	ST70Q03	No of <class period> p/wk - <Science>
#178	ST71Q01	No of ALL <class period> a week

```
